Computer Science House Constitution

### 2024-02-28 constitution.tex
Resolves #46 - Review Responsibilities of OpComm Director (#154)
* Updated responsibilities of opcomm director

* Fixed wording
134 Define intro process (#152)
* Fixed wording of definition of intro process

* Updated wording

\begin{enumerate}
	\item Chairperson - Chair
	\item Evaluations - Evals
	\item Research and Development - R\&D
	\item House Improvements - IMPs
	\item Operational Communications - OpComm
	\item House History - History
	\item Public Relations - PR
	\item Socials - Social
	\item Financials - Financial
	\item Root Type Person - RTP
	\item Introductory - Intro
	\item Executive Board - E-Board
	\item Department of Residence Life - ResLife
	\item Constitutional Maintainer - Maintainer
\end{enumerate}

@@

\asubsection{Responsibilities of the OpComm Director}
\begin{enumerate}
	\item To represent the RTPs at E-Board Meetings and at House Meetings
	\item To report the status of the House computer systems and network to E-Board and House members
	\item To vote on issues presented to E-Board
\end{enumerate}

@@

\asubsubsection{The Introductory Process}
The Intro Process is designed to provide an easy means for Intro Members to meet existing House members, learn history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.

>>>>

\begin{enumerate}
	\item Chairperson - Chair
	\item Evaluations - Evals
	\item Research and Development - R\&D
	\item House Improvements - IMPs
	\item Operational Communications - OpComm
	\item House History - History
	\item Public Relations - PR
	\item Socials - Social
	\item Financials - Financial
	\item Executive Board - E-Board
	\item Root Type Person - RTP
	\item Constitutional Maintainer - Maintainer
	\item Introductory - Intro
	\item Department of Residence Life - ResLife
\end{enumerate}

@@

\asubsection{Responsibilities of the OpComm Director}
\begin{enumerate}
	\item To represent the RTPs at E-Board Meetings and at House Meetings
	\item To report the status of the House computer systems and network to E-Board and House members
	\item To facilitate communications with RIT Information and Technology Services
	\item To vote on issues presented to E-Board
\end{enumerate}

@@

\asubsubsection{The Introductory Process}
The Intro Process allows Intro Members to learn about House and demonstrate their interest in becoming Active Members. During this period, Intro Members will meet existing House Members, learn House History, and be evaluated for Active Membership by existing House members.
